Optimal management of a stochastically varying population when policy adjustment is costly

### 2015-01-19 manuscripts/manuscript.Rmd
tuna citations

```{r Figure_1, fig.cap="Estimated stock abundances (top panels) show much greater variation than the corresponding harvest policies (bottom).  Left panels: ICCAT Stock assessments and Total Allowable Catch (TAC, before adjustments for national underages and overages) for bluefin tuna, 1987 - 2007. Right panels: SEDAR stock assessments and annual quotas for south Atlantic snowy grouper.", fig.width=6, fig.height=4, dev=c("pdf", "svg", "png"), cache=FALSE}
tuna <- read.csv("components/data/tuna.csv")
grouper <- read.csv("components/data/grouper.csv")

@@

To illustrate this tradeoff, we use an example from fisheries
management. Figure 1, top-left panel, shows a time series for the
estimated population size, represented as spawning stock biomass, of
west Atlantic bluefin tuna (_Thunnus thynnus_, henceforth bluefin) from
a recent stock assessment [@ICCAT20XX].  The bottom-left panel 
shows the catch quota (Total Allowable Catch or TAC, before being adjusted
for overages or underages in the catch of each country in the previous year)
for the stock as set by the relevant
management agency [@ICCAT20XX]. Despite the estimated population size
declining by XX% between YYYY and ZZZZ, the quota was not changed during
this period. Instead, the quota only changed occasionally and in between
times was left unaltered. Fishery management decisions regarding this
species can be highly contentious (@Safina1998, @Sissenwine1998,
@Porch2005). Moreover, the stock is fished by fleets from many nations
with quotas being set by a multilaterial management agency through a
process of negotiation. As such, we might reasonably anticipate that
for this species there could be substantial transaction costs involved
in reaching agreement over any quota change, or constraints on the frequency
with which the those changes could occur.  Either could contribute to
the observed quota stability. Such patterns of variable stocks managed
under far less variable quotas are extremely common; for instance, 
in the management of south Atlantic snowy grouper (_Epinephelus niveatus_) 
shown in the right-hand panels [@SEDAR2013]. More generally, reviews by @Biais1995 and
@Patterson2007a document many cases where changes in catch
quotas that a management agency set were more modest than changes that
would be recommended just by considering variations in stock abundance.

@@

```{r Figure_3, dependson="tidy", fig.cap="Example realization of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs. When costs vary linearly with the size of the adjustment ($\\Pi_1$), periods with no adjustment are more common than if adjustments were free.  When costs vary quadratically with adjustment size ($\\Pi_2$), small adjustments are relatively cheap and thus the resulting optimal policy always changes, but by a smaller amount than if adjustments were free.  When adjustments incur a fixed fee independent of size ($\\Pi_$), the optimal strategy either remains unchanged or overshoots the cost-free optimum. ", fig.height=5, fig.width=8, cache = fig.cache, dev=c("pdf", "svg", "png")}

>>>>

```{r Figure_1, fig.cap="Estimated stock abundances (top panels) show much greater variation than the corresponding harvest policies (bottom).  Left panels: ICCAT Stock assessments and Total Allowable Catch (TAC, before adjustments for national underages and overages) for bluefin tuna, 1982 - 2007. Right panels: SEDAR stock assessments and annual quotas for south Atlantic snowy grouper.", fig.width=6, fig.height=4, dev=c("pdf", "svg", "png"), cache=FALSE}
tuna <- read.csv("components/data/tuna.csv")
grouper <- read.csv("components/data/grouper.csv")

@@

To illustrate this tradeoff, we use an example from fisheries
management. Figure 1, top-left panel, shows a time series for the
estimated population size, represented as spawning stock biomass, of
west Atlantic bluefin tuna (_Thunnus thynnus_, henceforth bluefin) from
a recent stock assessment [@ICCAT2009a].  The bottom-left panel 
shows the catch quota (Total Allowable Catch or TAC, before being adjusted
for overages or underages in the catch of each country in the previous year)
for the stock as set by the relevant
management agency [@ICCAT2009a]. Despite the estimated population size
declining by `r 1 - min(tuna$stock)/max(tuna$stock)`% between 1982 and 1991, the quota was not changed during
this period. Instead, the quota only changed occasionally and in between
times was left unaltered. Fishery management decisions regarding this
species can be highly contentious (@Safina1998, @Sissenwine1998,
@Porch2005). Moreover, the stock is fished by fleets from many nations
with quotas being set by a multilaterial management agency through a
process of negotiation. As such, we might reasonably anticipate that
for this species there could be substantial transaction costs involved
in reaching agreement over any quota change, or constraints on the frequency
with which the those changes could occur.  Either could contribute to
the observed quota stability. Such patterns of variable stocks managed
under far less variable quotas are extremely common; for instance, 
in the management of south Atlantic snowy grouper (_Epinephelus niveatus_) 
shown in the right-hand panels [@SEDAR2013]. More generally, reviews by @Biais1995 and
@Patterson2007a document many cases where changes in catch
quotas that a management agency set were more modest than changes that
would be recommended just by considering variations in stock abundance.

@@

```{r Figure_3, dependson="tidy", fig.cap="Example realization of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs. When costs vary linearly with the size of the adjustment ($\\Pi_1$), periods with no adjustment are more common than if adjustments were free.  When costs vary quadratically with adjustment size ($\\Pi_2$), small adjustments are relatively cheap and thus the resulting optimal policy always changes, but by a smaller amount than if adjustments were free.  When adjustments incur a fixed fee independent of size ($\\Pi_3$), the optimal strategy either remains unchanged or overshoots the cost-free optimum. ", fig.height=5, fig.width=8, cache = fig.cache, dev=c("pdf", "svg", "png")}
